How to Avoid OOTA Without Really Trying

### 2025-03-06 paper/ootavacuous.tex
ootavacuous: Call out further benefits of modular relaxed dependencies
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Other researchers recommend various procedures to identify and avoid OOTA
cycles~\cite{Lahav:2017:RSC:3062341.3062352,Sinclair:2017:CAR:3079856.3080206,Lee:10.1145/3385412.3386010,MarkBatty2019ModularRelaxedDependenciesOOTA},
but none of these have been accepted by C++ implementers.
As of 2024, Mark Batty is working on modular relaxed dependencies,
which may have the added ability of checking compiler
optimizations~\cite{JayRichards2024SymbolicMrder}.

>>>>

Other researchers recommend various procedures to identify and avoid OOTA
cycles~\cite{Lahav:2017:RSC:3062341.3062352,Sinclair:2017:CAR:3079856.3080206,Lee:10.1145/3385412.3386010,MarkBatty2019ModularRelaxedDependenciesOOTA},
but none of these have been accepted by C++ implementers.
As of 2024, Mark Batty is working on modular relaxed dependencies,
which may have the added benefit of checking compiler
optimizations~\cite{JayRichards2024SymbolicMrder}, which is a portion
of the OOTA problem that is out of scope for this paper.\footnote{
	But please see Section~\ref{sec:Merging Quasi-Volatile Loads}.}
